Gravitational waves from colliding black holes

### 2017-04-05 Report/Draft/draft.tex
Updated report structure

\begin{abstract}

\end{abstract}

\section{Introduction}
Gravitational wave history and fundamental theory
\subsection{LIGO}
Fundamentals of detector
\subsection{Bayesian inference}
Theory used for PE
\subsection{MCMC}
\section{Matching}
\section{Software injections}
\section{Conclusions and implications}

>>>>

\begin{abstract}
Words
\end{abstract}

\section{Introduction}
Gravitational wave history
\subsection{Gravitational Waves}
Fundamental theory
\subsection{LIGO}
Overview of detectors
\subsection{Precession}
Precessing binaries and effective spin parameters
\subsection{Bayesian Inference}
Bayes theorem and how it is used in PE
\subsection{MCMC}
Overview of MCMCs that will be used for inference
\subsection{Astrophysical implications}
Binary formation models and how estimating chi p is significant for distinguishing bewteen them

\section{Matching}
Describe matching, and how matches are used to run targeted software injections.
Then identify parameter combinations where we are particularly sensitive to chi p, and those where we are not
\section{Software injections}
Describe software injections
\subsection{Signal extraction}
Data whitening - basically LOSC stuff, how we go from raw data to a signal - move this to intro?
\subsection{Inference pipeline}
Describe the structure of the inference pipeline
\subsection{Inference runs}
Posteriors and discussion of inference results
\subsection{Impact of Virgo}
A look at how Virgo will influence PE, especially chi p estimation
\section{Conclusions and implications}
Summary of results on PE and estimation of chi p, and a prospect on Virgo's impact.
